Sun v Shade leaves (WTCIII)

### 2015-03-30 markdown/wtc_sunshade.Rmd
put captions below figures

* This figure shows the instantaneous response of g<sub>m</sub> in shade leaves when the lights are 'turned on'

```{r gm lights on}
#plot low vs high light shade leaves
plot(Photo~gm, data=gm_water, subset=leaflight=="shade-high", pch=16, col=lightscol, ylim=c(0,25), xlim=c(0,.4), 
     xlab=gmlab, ylab="", cex=1.25)
  points(Photo~gm, data=gm_water, subset=leaflight=="shade-low",pch=16, col=shacol, cex=1.25)
  legend("topright", lightleg, pch=16,inset = 0.02, col=lightlab) 
  legend("topleft", "Shade Leaves", bty='n') 
  title(ylab=satlab, mgp=ypos, cex=1.2)
```

* Here is a simple version of the paired comparisons.  Only shade low light and sun leaves are used (watered and drought treatments together). All leaf types are compared to sun leaves at ambient temperature treatment (x axis)

@@

#third panel
par(mar=c(5,7,0,2))
plot(gm_sp[[2]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[5], cex=2.5, ylab="", xlim=c(0,.5), ylim=c(0,.5),xlab=suatgm)   
abline(0,1, lty=2)
legend(.4,.45, pairlab[3], pch=21, pt.bg=paircol[3], pt.cex=2,bg="white",inset = 0.06) 
```

* Here we see a slight reduction in g<sub>m</sub> with increase in temperature, but only in sun leaves

@@

legend("topleft", c("sun", "shade"), pch=16,inset = 0.03, col=leafcol) 
title(ylab=gmlab, mgp=ypos, cex=1.2)
```

@@

* ACi curves were measured at saturating light for both sun and shade leaves.

@@

panderOptions("digits", 3)
pander(aci_leaf2, caption="Leaf Biochemistry")
```

* Here are predicted ACi curves for leaf types with temperature treatments. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment. ACi curves were taken once towards the end of the experiment on well watered trees.

@@

#plot
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l", lwd=2)
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellowgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellowgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  title(ylab=satlab, mgp=ypos)
```

* This figure shows the relationship between leaf N on an area basis and ${\delta}$^13^C between leaf types (chamber means).

@@

@@

 bar(par, c(leaf_type, month), parbar, col=c("yellowgreen", "green4"), xlab="", ylab="", ylim=c(0, 2000), 
     half.errbar=FALSE)
 title(ylab=parlab, mgp=ypos)

 ###LMA--------------------------------------------------------------------------------------------------
 lma <- read.csv("calculated_data/leaf_chemistry.csv")

@@

 bar(lma, c(leaf, Month), lmabar, col=c("yellowgreen", "green4"), xlab="", ylab="", ylim=c(0, 185), half.errbar=FALSE)
 title(ylab=lmalab, mgp=ypos)

>>>>

```{r gm lights on}
#plot low vs high light shade leaves
plot(Photo~gm, data=gm_water, subset=leaflight=="shade-high", pch=16, col=lightscol, ylim=c(0,25), xlim=c(0,.4), 
     xlab=gmlab, ylab="", cex=1.25)
  points(Photo~gm, data=gm_water, subset=leaflight=="shade-low",pch=16, col=shacol, cex=1.25)
  legend("topright", lightleg, pch=16,inset = 0.02, col=lightlab) 
  legend("topleft", "Shade Leaves", bty='n') 
  title(ylab=satlab, mgp=ypos, cex=1.2)
```
* This figure shows the instantaneous response of g<sub>m</sub> in shade leaves when the lights are 'turned on'

@@

#third panel
par(mar=c(5,7,0,2))
plot(gm_sp[[2]][,3]~gm_sp[[3]][,3], pch=21, bg=wa[5], cex=2.5, ylab="", xlim=c(0,.5), ylim=c(0,.5),xlab=suatgm)   
abline(0,1, lty=2)
legend(.4,.45, pairlab[3], pch=21, pt.bg=paircol[3], pt.cex=2,bg="white",inset = 0.06) 
```
* Here is a simple version of the paired comparisons.  Only shade low light and sun leaves are used (watered and drought treatments together). All leaf types are compared to sun leaves at ambient temperature treatment (x axis)

@@

legend("topleft", c("sun", "shade"), pch=16,inset = 0.03, col=leafcol) 
title(ylab=gmlab, mgp=ypos, cex=1.2)
```
* Here we see a slight reduction in g<sub>m</sub> with increase in temperature, but only in sun leaves

@@

@@

panderOptions("digits", 3)
pander(aci_leaf2, caption="Leaf Biochemistry")
```    
* ACi curves were measured at saturating light for both sun and shade leaves.

@@

#plot
plot(sunAT_sim$Ci, sunAT_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab=cilab, ylab="", type="l", lwd=2)
  points(sunET_sim$Ci, sunET_sim$ALEAF, col="forestgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  points(shaAT_sim$Ci, shaAT_sim$ALEAF, col="yellowgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2)
  points(shaET_sim$Ci, shaET_sim$ALEAF, col="yellowgreen", pch=21,  cex=1.1,xlab="Ci", ylab="", type="l", lwd=2, lty=2)
  legend("bottomright", leglab2, lty=c(1,2,1,2), lwd=2,col=colaci, pt.bg=col4,inset = 0.03)
  title(ylab=satlab, mgp=ypos)
```
* Here are predicted ACi curves for leaf types with temperature treatments. Both Vc<sub>max</sub> and J<sub>max</sub> are reduced in shade leaves with little effect of the temperature treatment. ACi curves were taken once towards the end of the experiment on well watered trees.

@@

```
* This figure shows the relationship between leaf N on an area basis and ${\delta}$^13^C between leaf types (chamber means).

@@

 bar(par, c(leaf_type, month), parbar, col=c("yellowgreen", "green4"), xlab="", ylab="", ylim=c(0, 2000), 
     half.errbar=FALSE)
 title(ylab=parlab, mgp=ypos)
```

```{r}
 ###LMA-
 lma <- read.csv("calculated_data/leaf_chemistry.csv")

@@

 bar(lma, c(leaf, Month), lmabar, col=c("yellowgreen", "green4"), xlab="", ylab="", ylim=c(0, 185), half.errbar=FALSE)
 title(ylab=lmalab, mgp=ypos)
```
